Supermartingales and Termination Analysis of Statistical PCF

### 2021-01-24 LICS21/confluent.tex
A few more \defn

With this notation, a more general reduction relation $\to$ can be defined.
\begin{definition}
\label{def:more general red}
The binary relation $\to$ is defined by the following rules, each is conditional on a redex occurring at position $\alpha$ in the term $M$:
\begin{align*}
  \text{if } M \mid \alpha = (\lambda x.N) V,\ & M \to M[N[V/x]/\alpha] \\
  \text{if } M \mid \alpha = \underline f (\underline r_1, \dots , \underline r_n),\ & M \to M[\underline{f(r_1,\dots,r_n)}/\alpha] \\
  \text{if } M \mid \alpha = \tY \lambda x. N,\ & M \to M[\lambda z. N[(\tY \lambda x. N)/x] z/\alpha]\\ \text{where }z&\text{ is not free in $N$}\\
  \text{if } M \mid \alpha = \tif{\underline r < 0}{N_1}{N_2},\ & M \to M[N_1/\alpha] \text{ where }r < 0 \\
  \text{if } M \mid \alpha = \tif{\underline r < 0}{N_1}{N_2},\ & M \to M[N_2/\alpha] \text{ where }r \geq 0 \\
  \text{if } M \mid \alpha = \tsample \text{ and $\lambda$ does}&\text{ not occur after $@_2$ or $\tY$ in $\alpha$},\\ & M \to M[\underline r/\alpha] \text{ where } r \in [0,1].
\end{align*}
In each of these cases, $M \mid \alpha$ is the \defn{redex}, and the reduction takes place at $\alpha$.
\end{definition}

@@

The domain of definition of the ranking functions also needs to be changed from the reachable terms $\mathit{Rch}(M)$ to the \emph{reachable terms with respect to the reduction strategy $r$},
\[
\begin{array}{l}
\mathit{Rch}_r(M) := \{N \mid \exists n, (N_i)_{0 \leq i \leq n} : {}\\
\qquad\qquad\qquad N_0 = M, N_n = N, N_i \to N_{i+1} \text{ at } r(N_i)\}.
\end{array}
\]

>>>>

With this notation, a more general reduction relation $\to$ can be defined.
\begin{definition}
\label{def:more general red}
The binary relation $\to$ is defined by the following rules, each is conditional on a redex occurring at position $\alpha$ in the term $M$:
\begin{align*}
  \text{if } M \mid \alpha = (\lambda x.N) V,\ & M \to M[N[V/x]/\alpha] \\
  \text{if } M \mid \alpha = \underline f (\underline r_1, \dots , \underline r_n),\ & M \to M[\underline{f(r_1,\dots,r_n)}/\alpha] \\
  \text{if } M \mid \alpha = \tY \lambda x. N,\ & M \to M[\lambda z. N[(\tY \lambda x. N)/x] z/\alpha]\\ \text{where }z&\text{ is not free in $N$}\\
  \text{if } M \mid \alpha = \tif{\underline r < 0}{N_1}{N_2},\ & M \to M[N_1/\alpha] \text{ where }r < 0 \\
  \text{if } M \mid \alpha = \tif{\underline r < 0}{N_1}{N_2},\ & M \to M[N_2/\alpha] \text{ where }r \geq 0 \\
  \text{if } M \mid \alpha = \tsample \text{ and $\lambda$ does}&\text{ not occur after $@_2$ or $\tY$ in $\alpha$},\\ & M \to M[\underline r/\alpha] \text{ where } r \in [0,1].
\end{align*}
In each of these cases, $M \mid \alpha$ is the \defn{redex}, and the \defn{reduction takes place at $\alpha$}.
\end{definition}

@@

The domain of definition of the ranking functions also needs to be changed from the reachable terms $\mathit{Rch}(M)$ to the \defn{reachable terms with respect to the reduction strategy $r$},
\[
\begin{array}{l}
\mathit{Rch}_r(M) := \{N \mid \exists n, (N_i)_{0 \leq i \leq n} : {}\\
\qquad\qquad\qquad N_0 = M, N_n = N, N_i \to N_{i+1} \text{ at } r(N_i)\}.
\end{array}
\]
